Demographic Shifts in Toronto's Homeless Population: Evaluating and Reassessing City Solutions

### 2024-09-27 paper/paper.qmd
cite styler

While other datasets, such as daily shelter occupancy, are available, they lack the demographic depth necessary for this study. Data loading, cleaning, and analysis were carried out in R [@citeR], utilizing packages like tidyverse [@tidy], here [@here], and knitr [@knitr]. This comprehensive approach ensures that our analysis accurately reflects the realities faced by individuals experiencing homelessness in Toronto.

>>>>

While other datasets, such as daily shelter occupancy, are available, they lack the demographic depth necessary for this study. Data loading, cleaning, and analysis were carried out in **R** [@citeR], with packages **tidyverse** [@tidy], **here** [@here], **styler** [@style], and **knitr** [@knitr]. This comprehensive approach ensures that our analysis accurately reflects the realities faced by individuals experiencing homelessness in Toronto.
